Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-31 forecast/paper/paper.tex
Rewordings from Jacob and others

However, rigorously vetting the details for more sophisticated models, as well
as the generalizability of our findings to different geographic resolutions,
both remain important directions for future study.  For example, in the
Supplementary Materials we show that for forecasting at the state level, the
benefits provided by indicators models over AR are generally less clear
(compared to those observed at the HRR level).  One hypothesis is that at the
state level, where the signal-to-noise ratio (SNR) is higher, AR performs even
better and provides a higher standard (when asking whether it can be improved
upon using indicators).  At the HRR level, where the SNR is lower, including the
indicators as additional linear features in the AR model probably delivers a
kind of variance reduction (just like averaging independent terms would) which 
contributes to improved accuracy.  But at a higher SNR, this variance
reduction becomes less important, and we may be compelled to use more
sophisticated modeling techniques to extract comparable value from the
indicators.

We reiterate the importance of using vintage data for rigorous backtesting. Data
sources that are relevant to public health surveillance are often subject to
revision, sometimes regularly (as in medical claims data) and sometimes
unpredictably (such as COVID-19 case reports).  When analyzing models that are
designed to predict future events, if we train these models and make predictions
using finalized data, then we are missing a big part of the story.  Not only
will our sense of accuracy be unrealistic, but certain models may degrade by a
greater or lesser extent when they are forced to work with vintage data, so 
backtesting with finalized data may lead us to make modeling decisions that are
suboptimal for true test-time performance.

>>>>

However, rigorously vetting the details for more sophisticated models, as well
as the generalizability of our findings to different geographic resolutions,
both remain important directions for future study.  For example, in the
Supplementary Materials we show that for forecasting at the state level, the
benefits of adding indicators to the AR model are generally less clear
(compared to those observed at the HRR level).  A plausible explanation: at the
state level, where the signal-to-noise ratio (SNR) is higher, AR performs better
overall and provides a higher standard (when asking whether it can be improved 
upon using indicators).  At the HRR level, where the SNR is lower, including the
indicators as additional linear features in the AR model probably delivers a
kind of variance reduction (just like averaging independent terms would) which 
contributes to improved accuracy.  But at a higher SNR, this variance
reduction becomes less important, and we may be compelled to use more
sophisticated modeling techniques to extract comparable value from the
indicators.

We reiterate the importance of using vintage data for rigorous backtesting. Data
sources that are relevant to public health surveillance are often subject to
revision, sometimes regularly (as in medical claims data) and sometimes
unpredictably (such as COVID-19 case reports).  When analyzing models that are
designed to predict future events, if we train these models and make predictions
using finalized data, then we are missing a big part of the story.  Not only
will our sense of accuracy be unrealistic, but certain models may degrade by a
greater or lesser extent when they are forced to reckon with vintage data, so  
backtesting on finalized data may lead us to make modeling decisions that are
suboptimal for true test-time performance.
